Insert title of project here

### 2022-03-30 Draft Report/Draft Project.Rmd
Update Draft Project.Rmd

---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r, initialize}
# Set your working directory
getwd()
knitr::opts_knit$set(root.dir = "~/Desktop/Duke MPP/Environ Data /Environmental_Data_Analytics_2022/")

@@

@@

## Question 1: <insert specific question here and add additional subsections for additional questions below, if needed>

@@

# References
<add references here if relevant, otherwise delete this section>

>>>>

---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman
---

```{=tex}
\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage
```
```{r, initialize}
# Set your working directory
getwd()
knitr::opts_knit$set(root.dir = "~/Desktop/Duke MPP/Environ Data /Environmental_Data_Analytics_2022/")

@@

## Potential research questions!!!

-   Write what you're thinking about!

@@

## Question 1: \<insert specific question here and add additional subsections for additional questions below, if needed>

@@

# References

\<add references here if relevant, otherwise delete this section>
